---
title: "EDA"
output: html_notebook
---

What decade has the most popular games and what genre is the game?
 

```{r}
# Necesarry Libraries 
library(readr)
install.packages("dplyr")
library(dplyr)
```

#Reading CSV
```{r}
dataforEDA <- read.csv(file = "steamdata.csv", header=TRUE, stringsAsFactors=FALSE)
head(dataforEDA)
View(dataforEDA)
```
The Source of the Data is Kaggle.
Source (https://www.kaggle.com/datasets/thedevastator/get-your-game-on-metacritic-recommendations-and?resourcedownload&select=games-features-edit.csv)
The DataFrame has many variable, however the the ones we are most interested in are
The Metacritic Score, ResponseName,and ReleaseDate

Note: We are only using one data source since all the necessary information is present in this table.

```{r}
#I have defined a game to be good if it has a metacritic score greter that 80.
proc = (
  dataforEDA %>%
    group_by(ResponseName) %>%
    summarise(
      n = n(),
      Metacritic 
    ) %>%
    filter(
      n > 1,
      Metacritic > 80
    ))


head(proc)
```

We now have a better idea of what we need to answer our research question. We have defined a game as popular
If it has a metacritic score of 80 and above. Thus we are one step closer to answering our research question.
Our next goal is to use our finding in this exercise and use it in our final draft to find which era had the most popular games.
